Einstein's gravity from a polynomial affine model

### 2016-01-27 MS.tex
Equations of Birkhoff written covariantly

In this Appendix, we will present a brief compendium of known (Riemannian) metric solutions of Eq.~\eqref{SimpleEOM} in four dimensions. None of these workis original ---except the analysis presented as example in Sec.~\ref{Ex:sch}, and can be found in Refs.~\cite{gray1978einstein,derdzinski1980classification,derdzinski1982compact,Derdzinski:1985,Besse}. Additionally, in Ref.~\cite{cahen2000symplectic} \hl{What is this...}

@@

%%\paragraph{}

\subsection{Explicit example: Schwarzschild metric, and Birkhoff theorem\label{Ex:sch}}

As a disclaimer, we clarify that the example below is a pseudo-Riemannian manifold.

%%\subsubsection{Schwarzschild metric}

@@

In this section it will be shown that a static and spherically symmetric metric, which solves the field equations~\eqref{SimpleEOM} is necessarily the $\Lambda$--Schwarzschild metric.

Consider first the simplest metric ansatz, whose line element is
\begin{equation}
  \de{s}^2 = - f(t,r) \de{t}^2 + \frac{ \de{r}^2 }{ f(t,r) } + r^2 \de{\Omega}^2.
  \label{simpleSchw}
\end{equation}
\begin{widetext}
  The nontrivial field equation for the ansatz~\eqref{simpleSchw} are
  \begin{dmath}
    \nabla_{[1} R_{0]0} = \frac{1}{2 \, r^{2} f^{3}} \Bigg( r^{2} f^{4} \frac{\partial^3}{\partial r^{3}}f + 2 \, r f^{4} \frac{\partial^2}{\partial r^{2}}f + r^{2} f^{2} \frac{\partial^3}{\partial t^{2}\partial r^{}}f - 4 \, r^{2} f \frac{\partial}{\partial t^{}}f \frac{\partial^2}{\partial t^{}\partial r^{}}f - 2 \, f^{4} \frac{\partial}{\partial r^{}}f + 2 \, {\left(3 \, r^{2} \frac{\partial}{\partial r^{}}f - 2 \, r f\right)} \frac{\partial}{\partial t^{}}f^{2} - 2 \, {\left(r^{2} f \frac{\partial}{\partial r^{}}f - r f^{2}\right)} \frac{\partial^2}{\partial t^{2}}f \Bigg) ,
    \label{e100}
  \end{dmath}
  \begin{dmath}
    \nabla_{[1} R_{0]1} = \frac{1}{2 \, r^{2} f^{5}} \Bigg( r^{2} f^{4} \frac{\partial^3}{\partial t^{}\partial r^{2}}f + 2 \, f^{4} \frac{\partial}{\partial t^{}}f + 6 \, r^{2} \frac{\partial}{\partial t^{}}f^{3} - 6 \, r^{2} f \frac{\partial}{\partial t^{}}f \frac{\partial^2}{\partial t^{2}}f + r^{2} f^{2} \frac{\partial^3}{\partial t^{3}}f \Bigg) .
    \label{e101}
  \end{dmath}
  \begin{dmath}
    \nabla_{[2} R_{0]2} = r \frac{\partial^2}{\partial t^{}\partial r^{}}f,
    \label{e202}
  \end{dmath}
  \begin{dmath}
    \nabla_{[2} R_{1]2} = \frac{1}{2 \, r f^{3}} \Bigg(r^{2} f^{3} \frac{\partial^2}{\partial r^{2}}f - 2 \, f^{4} + 2 \, r^{2} \frac{\partial}{\partial t^{}}f^{2} - r^{2} f \frac{\partial^2}{\partial t^{2}}f + 2 \, f^{3} \Bigg),
    \label{e212}
  \end{dmath}
  \begin{dmath}
    \nabla_{[3} R_{0]3} = r \sin\left({\theta}\right)^{2} \frac{\partial^2}{\partial t^{}\partial r^{}}f,
    \label{e303}
  \end{dmath}
  and
  \begin{dmath}
    \nabla_{[3} R_{1]3} = \frac{1}{2 \, r f^{3}} \Bigg(r^{2} f^{3} \frac{\partial^2}{\partial r^{2}}f - 2 \, f^{4} + 2 \, r^{2} \frac{\partial}{\partial t^{}}f^{2} - r^{2} f \frac{\partial^2}{\partial t^{2}}f + 2 \, f^{3}\Bigg) \sin\left({\theta}\right)^{2}.
    \label{e313}
  \end{dmath}
\end{widetext}
Even though four out of the six nontrivial field equations are independent, the system can be solve uniquely. First, Eq.~\eqref{e202} yields $f = T(t) + R(r)$. Then, one notices that Eq.~\eqref{e101} contains a term depending solely on $t$, which implies that $\dot{T}$ vanishes, i.e., $T$ is a constant. From here, Eq.~\eqref{e212} gets simpler enough to be solved and yields, \mbox{$R(r) = 1 - T + \frac{\alpha}{r} + \beta r^2$} or equivalently
\begin{equation}
  f(r) = 1 + \frac{\alpha}{r} + \beta r^2,
  \label{simplef}
\end{equation}
with $\alpha$ and $\beta$ integration constants. Finally, it can be checked that albeit Eq.~\eqref{e100} was not used, it is satisfied by Eq.~\eqref{simplef}.

@@

However, if one tries a metric ansatz with two different factors, say
\begin{equation}
  \de{s}^2 = - A(t,r) \de{t}^2 + \frac{ \de{r}^2 }{ B(t,r) } + r^2 \de{\Omega}^2,
  \label{ABmetric}
\end{equation}
the field equations are so complicated, that although hints on the solubility were found ---and yield to Eq.~\eqref{simplef} for both $A$ and $B$---, the uniqueness of the solution is far for been proved. The field equations for the metric~\eqref{ABmetric} are %%shown in Appendix~\ref{app:eqAB}.
\begin{widetext}
  %%  \section{\label{app:eqAB}Field equations for Schwarzschild metric with two factors}
  \begin{dmath}
    \nabla_{[1} R_{0]0} = \frac{1}{4 \, r^{2} B^{3} A^{2}} \Bigg( 2 \, r^{2} B^{4} \frac{\partial}{\partial r^{}}A^{3} + 2 \, r^{2} B^{4} A^{2} \frac{\partial^3}{\partial r^{3}}A + 2 \, r^{2} B^{2} A^{2} \frac{\partial^3}{\partial t^{2}\partial r^{}}B - 6 \, r^{2} B A^{2} \frac{\partial}{\partial t^{}}B \frac{\partial^2}{\partial t^{}\partial r^{}}B - r^{2} B^{2} A \frac{\partial}{\partial t^{}}B \frac{\partial^2}{\partial t^{}\partial r^{}}A + 6 \, {\left(r^{2} A^{2} \frac{\partial}{\partial r^{}}B - r B A^{2}\right)} \frac{\partial}{\partial t^{}}B^{2} - 2 \, {\left(r^{2} B^{3} A \frac{\partial}{\partial r^{}}B + r B^{4} A\right)} \frac{\partial}{\partial r^{}}A^{2} - 2 \, {\left(r^{2} B A^{2} \frac{\partial}{\partial r^{}}B - 2 \, r B^{2} A^{2}\right)} \frac{\partial^2}{\partial t^{2}}B - {\left(r^{2} B^{2} A \frac{\partial^2}{\partial t^{}\partial r^{}}B - 2 \, r^{2} B^{2} \frac{\partial}{\partial t^{}}B \frac{\partial}{\partial r^{}}A - {\left(r^{2} B A \frac{\partial}{\partial r^{}}B - 2 \, r B^{2} A\right)} \frac{\partial}{\partial t^{}}B\right)} \frac{\partial}{\partial t^{}}A + {\left(r^{2} B^{3} A^{2} \frac{\partial^2}{\partial r^{2}}B + 2 \, r B^{3} A^{2} \frac{\partial}{\partial r^{}}B - 4 \, B^{4} A^{2} + 3 \, r^{2} B A \frac{\partial}{\partial t^{}}B^{2} - 2 \, r^{2} B^{2} A \frac{\partial^2}{\partial t^{2}}B\right)} \frac{\partial}{\partial r^{}}A + {\left(3 \, r^{2} B^{3} A^{2} \frac{\partial}{\partial r^{}}B - 4 \, r^{2} B^{4} A \frac{\partial}{\partial r^{}}A + 4 \, r B^{4} A^{2}\right)} \frac{\partial^2}{\partial r^{2}}A \Bigg),
    \label{eq100}
  \end{dmath}

  \begin{dmath}
    \nabla_{[1} R_{0]1} = \frac{1}{4 \, r^{2} B^{4} A^{3}} \Bigg( 2 \, r^{2} B^{4} A^{2} \frac{\partial^3}{\partial t^{}\partial r^{2}}A + r^{2} B^{3} A^{2} \frac{\partial^2}{\partial t^{}\partial r^{}}B \frac{\partial}{\partial r^{}}A - r^{2} B^{3} A \frac{\partial}{\partial t^{}}B \frac{\partial}{\partial r^{}}A^{2} + 2 \, r^{2} B^{3} A^{2} \frac{\partial}{\partial t^{}}B \frac{\partial^2}{\partial r^{2}}A + 4 \, B^{3} A^{3} \frac{\partial}{\partial t^{}}B + 6 \, r^{2} A^{2} \frac{\partial}{\partial t^{}}B^{3} - 8 \, r^{2} B A^{2} \frac{\partial}{\partial t^{}}B \frac{\partial^2}{\partial t^{2}}B + 2 \, r^{2} B^{2} A^{2} \frac{\partial^3}{\partial t^{3}}B + 2 \, r^{2} B^{2} \frac{\partial}{\partial t^{}}B \frac{\partial}{\partial t^{}}A^{2} - r^{2} B^{2} A \frac{\partial}{\partial t^{}}B \frac{\partial^2}{\partial t^{2}}A - {\left(r^{2} B^{3} A \frac{\partial}{\partial r^{}}B \frac{\partial}{\partial r^{}}A - 2 \, r^{2} B^{4} \frac{\partial}{\partial r^{}}A^{2} + 2 \, r^{2} B^{4} A \frac{\partial^2}{\partial r^{2}}A - 4 \, r^{2} B A \frac{\partial}{\partial t^{}}B^{2} + 3 \, r^{2} B^{2} A \frac{\partial^2}{\partial t^{2}}B\right)} \frac{\partial}{\partial t^{}}A + {\left(r^{2} B^{3} A^{2} \frac{\partial}{\partial r^{}}B - 2 \, r^{2} B^{4} A \frac{\partial}{\partial r^{}}A\right)} \frac{\partial^2}{\partial t^{}\partial r^{}}A \Bigg),
    \label{eq101}
  \end{dmath}

  \begin{dmath}
    \nabla_{[2} R_{0]2} = \frac{1}{2 \, A^{2}} \Bigg( r A^{2} \frac{\partial^2}{\partial t^{}\partial r^{}}B + r B A \frac{\partial^2}{\partial t^{}\partial r^{}}A + r A \frac{\partial}{\partial t^{}}B \frac{\partial}{\partial r^{}}A - r B \frac{\partial}{\partial t^{}}A \frac{\partial}{\partial r^{}}A \Bigg),
    \label{eq202}
  \end{dmath}

  \begin{dmath}
    \nabla_{[2} R_{1]2} = \frac{1}{4 \, r B^{2} A^{2}} \Bigg( 2 \, r^{2} B^{2} A^{2} \frac{\partial^2}{\partial r^{2}}B + r^{2} B^{2} A \frac{\partial}{\partial r^{}}B \frac{\partial}{\partial r^{}}A - r^{2} B^{3} \frac{\partial}{\partial r^{}}A^{2} + 3 \, r^{2} A \frac{\partial}{\partial t^{}}B^{2} - 2 \, r^{2} B A \frac{\partial^2}{\partial t^{2}}B + r^{2} B \frac{\partial}{\partial t^{}}B \frac{\partial}{\partial t^{}}A - 4 \, {\left(B^{3} - B^{2}\right)} A^{2} \Bigg),
    \label{eq212}
  \end{dmath}

  \begin{align*}
    \nabla_{[3} R_{0]3} &= \nabla_{[2} R_{0]2} \sin\left({\theta}\right)^{2}, &
    \nabla_{[3} R_{1]3} &= \nabla_{[2} R_{1]2} \sin\left({\theta}\right)^{2},
  \end{align*}
which are very complex, and ---to our knowledge--- are not possible to solve in general.
\end{widetext}

>>>>

In this Appendix, we will present a brief compendium of known (Riemannian) metric solutions of Eq.~\eqref{SimpleEOM} in four dimensions. None of these workis original ---except the analysis presented as example in Sec.~\ref{Ex:sch}, and can be found in Refs.~\cite{gray1978einstein,derdzinski1980classification,derdzinski1982compact,Derdzinski:1985,Besse}.

@@

Although the above are examples of manifolds with parallel Ricci within the context of ``Riemannian'' geometries, examples of connnections with parallel Ricci can be found in symplectic geometries, see Ref.~\cite{cahen2000symplectic}.

\section{Explicit example: Schwarzschild ansatz, and (incomplete) Birkhoff theorem\label{Ex:sch}}

%% As a disclaimer\hl{What is this... Should this be dropped?}, we clarify that the example below is a pseudo-Riemannian manifold.

%% \subsubsection{Schwarzschild metric}

@@

In this section we show that the simplest ansatz of a static and spherically symmetric metric, which solves the Eq.~\eqref{SimpleEOM} is necessarily the $\Lambda$--Schwarzschild metric. This should be taken as a first step toward a Birkhoff theorem, despite the fact that a complete proof is far from been achieved.

Consider first the simplest metric ansatz, whose line element is
\begin{equation}
  \de{s}^2 = - f(t,r) \de{t}^2 + \frac{ \de{r}^2 }{ f(t,r) } + r^2 \de{\Omega}^2.
  \label{simpleSchw}
\end{equation}
\begin{widetext}
  The nontrivial field equation for the ansatz~\eqref{simpleSchw} are
  \begin{dmath}
    \nabla_{[\mu} R_{\nu]\lambda} = \frac{1}{2 \, r^{2} f^{3}} \Bigg( r^{2} f^{4} \frac{\partial^3}{\partial r^{3}}f + 2 \, r f^{4} \frac{\partial^2}{\partial r^{2}}f + r^{2} f^{2} \frac{\partial^3}{\partial t^{2}\partial r^{}}f - 4 \, r^{2} f \frac{\partial}{\partial t^{}}f \frac{\partial^2}{\partial t^{}\partial r^{}}f - 2 \, f^{4} \frac{\partial}{\partial r^{}}f + 2 \, {\left(3 \, r^{2} \frac{\partial}{\partial r^{}}f - 2 \, r f\right)} \frac{\partial}{\partial t^{}}f^{2} - 2 \, {\left(r^{2} f \frac{\partial}{\partial r^{}}f - r f^{2}\right)} \frac{\partial^2}{\partial t^{2}}f \Bigg) \,
    \delta_{\mu\nu}^{10} \delta_\lambda^0
    +
    \frac{1}{2 \, r^{2} f^{5}} \Bigg( r^{2} f^{4} \frac{\partial^3}{\partial t^{}\partial r^{2}}f + 2 \, f^{4} \frac{\partial}{\partial t^{}}f + 6 \, r^{2} \frac{\partial}{\partial t^{}}f^{3} - 6 \, r^{2} f \frac{\partial}{\partial t^{}}f \frac{\partial^2}{\partial t^{2}}f + r^{2} f^{2} \frac{\partial^3}{\partial t^{3}}f \Bigg) \,
    \delta_{\mu\nu}^{10} \delta_\lambda^1
    +
    r \frac{\partial^2}{\partial t^{}\partial r^{}}f \,
    \Big( \delta_{\mu\nu}^{20} \delta_\lambda^2 + \sin^2(\theta) \delta_{\mu\nu}^{30} \delta_\lambda^3 \Big)
    +
    \frac{1}{2 \, r f^{3}} \Bigg(r^{2} f^{3} \frac{\partial^2}{\partial r^{2}}f - 2 \, f^{4} + 2 \, r^{2} \frac{\partial}{\partial t^{}}f^{2} - r^{2} f \frac{\partial^2}{\partial t^{2}}f + 2 \, f^{3} \Bigg) \,
    \Big( \delta_{\mu\nu}^{21} \delta_\lambda^2 + \sin^2(\theta) \delta_{\mu\nu}^{31} \delta_\lambda^3 \Big)
    = 0
  \end{dmath}
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  %%   \begin{dmath}
  %%   \nabla_{[1} R_{0]0} = \frac{1}{2 \, r^{2} f^{3}} \Bigg( r^{2} f^{4} \frac{\partial^3}{\partial r^{3}}f + 2 \, r f^{4} \frac{\partial^2}{\partial r^{2}}f + r^{2} f^{2} \frac{\partial^3}{\partial t^{2}\partial r^{}}f - 4 \, r^{2} f \frac{\partial}{\partial t^{}}f \frac{\partial^2}{\partial t^{}\partial r^{}}f - 2 \, f^{4} \frac{\partial}{\partial r^{}}f + 2 \, {\left(3 \, r^{2} \frac{\partial}{\partial r^{}}f - 2 \, r f\right)} \frac{\partial}{\partial t^{}}f^{2} - 2 \, {\left(r^{2} f \frac{\partial}{\partial r^{}}f - r f^{2}\right)} \frac{\partial^2}{\partial t^{2}}f \Bigg) ,
  %%   \label{e100}
  %% \end{dmath}
  %% \begin{dmath}
  %%   \nabla_{[1} R_{0]1} = \frac{1}{2 \, r^{2} f^{5}} \Bigg( r^{2} f^{4} \frac{\partial^3}{\partial t^{}\partial r^{2}}f + 2 \, f^{4} \frac{\partial}{\partial t^{}}f + 6 \, r^{2} \frac{\partial}{\partial t^{}}f^{3} - 6 \, r^{2} f \frac{\partial}{\partial t^{}}f \frac{\partial^2}{\partial t^{2}}f + r^{2} f^{2} \frac{\partial^3}{\partial t^{3}}f \Bigg) .
  %%   \label{e101}
  %% \end{dmath}
  %% \begin{dmath}
  %%   \nabla_{[2} R_{0]2} = r \frac{\partial^2}{\partial t^{}\partial r^{}}f,
  %%   \label{e202}
  %% \end{dmath}
  %% \begin{dmath}
  %%   \nabla_{[2} R_{1]2} = \frac{1}{2 \, r f^{3}} \Bigg(r^{2} f^{3} \frac{\partial^2}{\partial r^{2}}f - 2 \, f^{4} + 2 \, r^{2} \frac{\partial}{\partial t^{}}f^{2} - r^{2} f \frac{\partial^2}{\partial t^{2}}f + 2 \, f^{3} \Bigg),
  %%   \label{e212}
  %% \end{dmath}
  %% %% \begin{dmath}
  %% %%   \nabla_{[3} R_{0]3} = r \sin\left({\theta}\right)^{2} \frac{\partial^2}{\partial t^{}\partial r^{}}f,
  %% %%   \label{e303}
  %% %% \end{dmath}
  %% %% and
  %% %% \begin{dmath}
  %% %%   \nabla_{[3} R_{1]3} = \frac{1}{2 \, r f^{3}} \Bigg(r^{2} f^{3} \frac{\partial^2}{\partial r^{2}}f - 2 \, f^{4} + 2 \, r^{2} \frac{\partial}{\partial t^{}}f^{2} - r^{2} f \frac{\partial^2}{\partial t^{2}}f + 2 \, f^{3}\Bigg) \sin\left({\theta}\right)^{2}.
  %% %%   \label{e313}
  %% %% \end{dmath}
  %% \begin{align}
  %%   \nabla_{[3} R_{0]3} &= \sin\left({\theta}\right)^{2} \nabla_{[2} R_{0]2}, &
  %%   \nabla_{[3} R_{1]3} &= \sin\left({\theta}\right)^{2} \nabla_{[2} R_{1]2}.
  %% \end{align}
\end{widetext}
Even though four out of the six nontrivial field equations are independent, the system can be solve uniquely. First, the component along the $(\mu\nu\lambda) = (2,0,2)$ yields $f = T(t) + R(r)$. Then, one notices that the equation along $(\mu\nu\lambda) = (1,0,1)$ contains a term depending solely on $t$, which implies that $\dot{T}$ vanishes, i.e., $T$ is a constant. From here, the equation for $(\mu\nu\lambda) = (2,1,2)$ gets simple enough to be solved and yields, \mbox{$R(r) = 1 - T + \frac{\alpha}{r} + \beta r^2$} or equivalently
\begin{equation}
  f(r) = 1 + \frac{\alpha}{r} + \beta r^2,
  \label{simplef}
\end{equation}
with $\alpha$ and $\beta$ integration constants. Finally, it can be checked that albeit the equation along the components $(\mu,\nu,\lambda) = (1,0,0)$ was not used, it is satisfied by Eq.~\eqref{simplef}.

@@

However, if one tries a metric ansatz with two different factors, say
\begin{equation}
  \de{s}^2 = - A(t,r) \de{t}^2 + \frac{ \de{r}^2 }{ B(t,r) } + r^2 \de{\Omega}^2,
  \label{ABmetric}
\end{equation}
the field equations are so complicated, that although hints on the solubility were found ---and yield to Eq.~\eqref{simplef} for both $A$ and $B$---, the uniqueness of the solution is far for been proved. The field equations for the metric~\eqref{ABmetric} are %%shown in Appendix~\ref{app:eqAB}.
\begin{widetext}
  \begin{dmath}
    \nabla_{[\mu} R_{\nu]\lambda} = \frac{1}{4 \, r^{2} B^{3} A^{2}} \Bigg( 2 \, r^{2} B^{4} \frac{\partial}{\partial r^{}}A^{3} + 2 \, r^{2} B^{4} A^{2} \frac{\partial^3}{\partial r^{3}}A + 2 \, r^{2} B^{2} A^{2} \frac{\partial^3}{\partial t^{2}\partial r^{}}B - 6 \, r^{2} B A^{2} \frac{\partial}{\partial t^{}}B \frac{\partial^2}{\partial t^{}\partial r^{}}B - r^{2} B^{2} A \frac{\partial}{\partial t^{}}B \frac{\partial^2}{\partial t^{}\partial r^{}}A + 6 \, {\left(r^{2} A^{2} \frac{\partial}{\partial r^{}}B - r B A^{2}\right)} \frac{\partial}{\partial t^{}}B^{2} - 2 \, {\left(r^{2} B^{3} A \frac{\partial}{\partial r^{}}B + r B^{4} A\right)} \frac{\partial}{\partial r^{}}A^{2} - 2 \, {\left(r^{2} B A^{2} \frac{\partial}{\partial r^{}}B - 2 \, r B^{2} A^{2}\right)} \frac{\partial^2}{\partial t^{2}}B - {\left(r^{2} B^{2} A \frac{\partial^2}{\partial t^{}\partial r^{}}B - 2 \, r^{2} B^{2} \frac{\partial}{\partial t^{}}B \frac{\partial}{\partial r^{}}A - {\left(r^{2} B A \frac{\partial}{\partial r^{}}B - 2 \, r B^{2} A\right)} \frac{\partial}{\partial t^{}}B\right)} \frac{\partial}{\partial t^{}}A + {\left(r^{2} B^{3} A^{2} \frac{\partial^2}{\partial r^{2}}B + 2 \, r B^{3} A^{2} \frac{\partial}{\partial r^{}}B - 4 \, B^{4} A^{2} + 3 \, r^{2} B A \frac{\partial}{\partial t^{}}B^{2} - 2 \, r^{2} B^{2} A \frac{\partial^2}{\partial t^{2}}B\right)} \frac{\partial}{\partial r^{}}A + {\left(3 \, r^{2} B^{3} A^{2} \frac{\partial}{\partial r^{}}B - 4 \, r^{2} B^{4} A \frac{\partial}{\partial r^{}}A + 4 \, r B^{4} A^{2}\right)} \frac{\partial^2}{\partial r^{2}}A \Bigg) \,
    \delta_{\mu\nu}^{10} \delta_\lambda^0
    +
    \frac{1}{4 \, r^{2} B^{4} A^{3}} \Bigg( 2 \, r^{2} B^{4} A^{2} \frac{\partial^3}{\partial t^{}\partial r^{2}}A + r^{2} B^{3} A^{2} \frac{\partial^2}{\partial t^{}\partial r^{}}B \frac{\partial}{\partial r^{}}A - r^{2} B^{3} A \frac{\partial}{\partial t^{}}B \frac{\partial}{\partial r^{}}A^{2} + 2 \, r^{2} B^{3} A^{2} \frac{\partial}{\partial t^{}}B \frac{\partial^2}{\partial r^{2}}A + 4 \, B^{3} A^{3} \frac{\partial}{\partial t^{}}B + 6 \, r^{2} A^{2} \frac{\partial}{\partial t^{}}B^{3} - 8 \, r^{2} B A^{2} \frac{\partial}{\partial t^{}}B \frac{\partial^2}{\partial t^{2}}B + 2 \, r^{2} B^{2} A^{2} \frac{\partial^3}{\partial t^{3}}B + 2 \, r^{2} B^{2} \frac{\partial}{\partial t^{}}B \frac{\partial}{\partial t^{}}A^{2} - r^{2} B^{2} A \frac{\partial}{\partial t^{}}B \frac{\partial^2}{\partial t^{2}}A - {\left(r^{2} B^{3} A \frac{\partial}{\partial r^{}}B \frac{\partial}{\partial r^{}}A - 2 \, r^{2} B^{4} \frac{\partial}{\partial r^{}}A^{2} + 2 \, r^{2} B^{4} A \frac{\partial^2}{\partial r^{2}}A - 4 \, r^{2} B A \frac{\partial}{\partial t^{}}B^{2} + 3 \, r^{2} B^{2} A \frac{\partial^2}{\partial t^{2}}B\right)} \frac{\partial}{\partial t^{}}A + {\left(r^{2} B^{3} A^{2} \frac{\partial}{\partial r^{}}B - 2 \, r^{2} B^{4} A \frac{\partial}{\partial r^{}}A\right)} \frac{\partial^2}{\partial t^{}\partial r^{}}A \Bigg) \,
    \delta_{\mu\nu}^{10} \delta_\lambda^1
    +
    \frac{1}{2 \, A^{2}} \Bigg( r A^{2} \frac{\partial^2}{\partial t^{}\partial r^{}}B + r B A \frac{\partial^2}{\partial t^{}\partial r^{}}A + r A \frac{\partial}{\partial t^{}}B \frac{\partial}{\partial r^{}}A - r B \frac{\partial}{\partial t^{}}A \frac{\partial}{\partial r^{}}A \Bigg) \,
    \Big( \delta_{\mu\nu}^{20} \delta_\lambda^2 + \sin^2(\theta) \delta_{\mu\nu}^{30} \delta_\lambda^3 \Big)
    +
    \frac{1}{4 \, r B^{2} A^{2}} \Bigg( 2 \, r^{2} B^{2} A^{2} \frac{\partial^2}{\partial r^{2}}B + r^{2} B^{2} A \frac{\partial}{\partial r^{}}B \frac{\partial}{\partial r^{}}A - r^{2} B^{3} \frac{\partial}{\partial r^{}}A^{2} + 3 \, r^{2} A \frac{\partial}{\partial t^{}}B^{2} - 2 \, r^{2} B A \frac{\partial^2}{\partial t^{2}}B + r^{2} B \frac{\partial}{\partial t^{}}B \frac{\partial}{\partial t^{}}A - 4 \, {\left(B^{3} - B^{2}\right)} A^{2} \Bigg) \,
    \Big( \delta_{\mu\nu}^{21} \delta_\lambda^2 + \sin^2(\theta) \delta_{\mu\nu}^{31} \delta_\lambda^3 \Big)
    = 0,
  \end{dmath}
\end{widetext}
which are very complex, and ---to our knowledge--- these are not possible to solve in general. Nonetheless, the symmetries in some of the components of these equations seems to favour the relation $A = B$ as solution. In addition, we found a very interesting reference in which a proof of the Birkhoff theorem is given for an Einstein--Cartan theory coupled with the gravitational Yang--Mills~\cite{Ramaswamy:1979zz}, which support the hand-waving symmetry argument above.
